Fish Data For Ji Zhou

### 2022-05-18 Fish Data Analysis/Ji_Zhou_Data.Rmd
Back before adding roup level features
Update before I do my work making the 3D processor

comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
                           filter(Distance <= 4) %>%
                           filter(Speed_Diff <= 6) %>% 
                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0)) %>%
                           mutate(Angle = fold_angle_0_360_to_0_180(Angle))

@@

Fish Size:

  Small Fish: 
    Length: 
    Width:
    Height:

  Big Fish: 
    Length: 
    Width:
    Height:

@@

>>>>

indiv_data <- read.csv("Fish_Individual_Values.csv")
indiv_data <- na.omit(indiv_data)

# comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
#                            mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
#                            mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
#                            mutate(Heading_Diff = abs(Heading_Diff)) %>%
#                            filter(Distance <= 4) %>%
#                            filter(Speed_Diff <= 6) %>% 
#                            mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
#                            mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
#                            mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0)) %>%
#                            mutate(Angle = fold_angle_0_360_to_0_180(Angle))

@@

Fish Size (cm):

  Fish 1: 
    Length: 8.2
    Width:  0.8
    Height: 1.8

  Fish 2: 
    Length: 6.7
    Width:  0.8
    Height: 1.7

  Fish 3: 
    Length: 7.3
    Width:  0.7
    Height: 1.6

  Fish 4: 
    Length: 6.6
    Width:  0.7
    Height: 1.4

@@

```{r}
ggplot(indiv_data, aes(X, Y) ) +
  geom_bin2d(bins = 15) +
  facet_wrap(~ Flow + Ablation + Darkness) +
  scale_fill_continuous(type = "viridis") +
  theme_light()
```
